Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-20 article.rnw
Elaborate upon the meaning of the result of the Monte Carlo permutation test on the Akaike weights.
Add a section to the methods on the coclassification matrices and associated tests.

%TODO: Explain the coclassification matrices and the tests.

%TODO: Use Terry et al. table S1 for additional classification information. The two species that coclassify in both columns and rows are substantially larger.

@@

Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics$aic)}}; neither the best nor worst overall models had equivalently grouped rows and columns.
The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
% DBS: I think the last sentence above needs a bit of elaboration here OR the usefulness of this "test" should be explained in the Methods in the section that discusses how we examined aspects of parsimony.

>>>>

\subsubsection{Coclassification matrices}

To summarise the results, the Akaike weights were used to generate coclassification matrices, one for the row groupings and one for the column groupings.
Each cell of a coclassification matrix represents the coclassification of two species, and contains the total Akaike weight of models that place those two species in the same group.
As such, each cell represents the probability that the most parsimonious model is one that coclassifies those two species.

There are a number of possible ``null'' expectations for these matrices.
A neutral model approach would expect all species to be the same: every cell would be $1$.
If each species were expected to be unique, every off-diagonal cell would be $0$.
Alternatively, if every possible grouping were considered to be equally likely, every off-diagonal cell would be $\frac{B_{n-1}}{B_n}$: \probnum{\Sexpr{numbers::bell(5)/numbers::bell(6)}} for six species.
Unfortunately, without a null distribution, it was impossible to test the empirical coclassification matrices against a null expectation.

However, we could test the coclassification matrices against one another.
By testing for correlation between the coclassification matrix for the the rows and that for the columns, we could test the assumption that it is appropriate to use the same grouping for both.
We did this using a Mantel test, as appropriate for similarity matrices.

We could also test the coclassification matrices for correlation with an expected dissimilarity matrix.
We calculated one such dissimilarity matrix based on a species trait: body size (as mean wet mass of female adults, obtained from \cite{terry2021natural}).
The trait difference matrix was calculated as absolute difference between trait values, while the coclassification matrices were converted to dissimilarity matrices by subtracting from $1$.
We performed a Mantel test for correlation between the trait distance matrix and each of the two coclassification dissimilarity matrices.

@@

Considering only models in which the rows and columns were grouped using the same grouping, the AIC values ranged from \aicnum{\Sexpr{min(brute_data$equivalently_grouped_statistics$aic)}} to \aicnum{\Sexpr{max(brute_data$equivalently_grouped_statistics$aic)}}; neither the best nor worst overall models had equivalently grouped rows and columns.
The total Akaike weight assigned to these models was \probnum{\Sexpr{brute_data$equivalently_grouped_weight}}; more than expected by chance (\probnum{\Sexpr{brute_data$equivalently_grouped_expected_weight}}), but not significantly so (Monte Carlo permutation test, $p=\probnum{\Sexpr{brute_data$equivalently_grouped_weight_p #$}}$).
This indicates that the most parsimonious model is not especially likely to be one that groups the rows and columns equivalently.
